Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments

### 2024-09-10 article/alt_article.tex
Update Paper
WIth Comments from GJ

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  authoryear,
  review,
  1p]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
\tnotetext[t2]{The authors would like to thank Enrique Pinzon an Joao Santos-Silva for their helpful comments and suggestions.}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments },
  pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
  pdfkeywords={Fixed effects, Linear heteroskedasticity, Location-scale
model, Quantile regression},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{Estimating Quantile Regressions with Multiple Fixed Effects
through Method of Moments \tnoteref{t1,t2}}
\author[1]{Fernando Rios-Avila%
\corref{cor1}%
}
 \ead{friosavi@levy.org} 
\author[2]{Leonardo Siles%
%
}
 \ead{leonardo.siles@ucb.edu.bo} 
\author[3]{Gustavo Canavire-Bacarreza%
%
}
 \ead{gcanavire@worldbank.org}

\affiliation[1]{organization={Levy Economics Institute of Bard
College},city={Annandale-on-Hudson,
NY},country={USA},countrysep={,},postcodesep={}}
\affiliation[2]{organization={Universidad Católica Boliviana},city={La
Paz},country={Bolivia},countrysep={,},postcodesep={}}
\affiliation[3]{organization={The World Bank},city={Washington,
D.C.},country={USA},countrysep={,},postcodesep={}}

\cortext[cor1]{Corresponding author}

\begin{abstract}
This paper proposes a new method to estimate quantile regressions with
multiple fixed effects. The method, which expands on the strategy
proposed by \citet{mss2019}, allows for the inclusion of multiple fixed
effects and provides various alternatives for the estimation of standard
errors. We provide Monte Carlo simulations to show the finite sample
properties of the proposed method in the presence of two sets of fixed
effects. Finally, we apply the proposed method to estimate the
determinants of the surplus of government as a share of GDP, allowing
for both time and country fixed effects.
\end{abstract}

\begin{keyword}
    Fixed effects \sep Linear heteroskedasticity \sep Location-scale
model \sep 
    Quantile regression
\end{keyword}
\end{frontmatter}

@@

In principle, under the assumption that data-generating process behind
the data is based on a multiplicative heteroskedastic process that is
linear in parameters \citep[\citet{he1997}, \citet{zhao2000},
\citet{cameron2005}]{mss2019}, the effect of a variable \(X\) on the
\(q_{th}\) quantile can be derived as the combination of a location
effect, and scale effect moderated by the quantile of an underlying
i.i.d. error. For statistical inference, MSS derives the asymptotic
distribution of the estimator, suggesting the use of bootstrap standard
errors, as well.

@@

\begin{table}

@@

\section{Illustrative application}\label{illustrative-application}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1235}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1111}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0864}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0864}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}@{}}
\caption{Determinants of Government Surpluses: Individual Fixed
Effects}\label{tbl-tb1}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
polityt
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
lyp
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
trade
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
p1564
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
p65
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
lspl
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
oil\_im
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
oil\_ex
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
ygap
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
polityt
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
lyp
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
trade
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
p1564
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
p65
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
lspl
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
oil\_im
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
oil\_ex
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
ygap
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Location & & & & & & & & & \\
~coeff & 0.116 & -0.715 & 0.030 & 0.121 & 0.028 & 0.691 & -0.047 &
-0.006 & 0.010 \\
~se\_gls & 0.046 & 0.540 & 0.008 & 0.033 & 0.070 & 0.035 & 0.008 & 0.022
& 0.028 \\
~se\_r & 0.047 & 0.597 & 0.008 & 0.031 & 0.070 & 0.037 & 0.007 & 0.017 &
0.021 \\
~se\_cl & 0.046 & 0.465 & 0.007 & 0.032 & 0.071 & 0.035 & 0.010 & 0.020
& 0.023 \\
Scale & & & & & & & & & \\
~coeff & -0.097 & -0.616 & 0.003 & 0.036 & 0.087 & -0.085 & 0.013 &
0.016 & -0.004 \\
~se\_gls & 0.032 & 0.371 & 0.005 & 0.023 & 0.048 & 0.024 & 0.006 & 0.015
& 0.019 \\
~se\_r & 0.031 & 0.398 & 0.005 & 0.020 & 0.049 & 0.025 & 0.005 & 0.010 &
0.015 \\
~se\_cl & 0.048 & 0.800 & 0.008 & 0.031 & 0.067 & 0.029 & 0.004 & 0.010
& 0.012 \\
Q25 & & & & & & & & & \\
~coeff & 0.191 & -0.239 & 0.028 & 0.093 & -0.039 & 0.756 & -0.057 &
-0.018 & 0.013 \\
~se\_gls & 0.059 & 0.684 & 0.010 & 0.042 & 0.088 & 0.045 & 0.010 & 0.027
& 0.035 \\
~se\_r & 0.056 & 0.656 & 0.008 & 0.036 & 0.086 & 0.040 & 0.010 & 0.020 &
0.025 \\
~se\_cl & 0.073 & 0.687 & 0.006 & 0.041 & 0.098 & 0.023 & 0.010 & 0.021
& 0.029 \\
Q50 & & & & & & & & & \\
~coeff & 0.108 & -0.765 & 0.030 & 0.124 & 0.035 & 0.684 & -0.046 &
-0.005 & 0.009 \\
~se\_gls & 0.046 & 0.535 & 0.007 & 0.033 & 0.069 & 0.035 & 0.008 & 0.022
& 0.027 \\
~se\_r & 0.046 & 0.593 & 0.008 & 0.031 & 0.069 & 0.036 & 0.007 & 0.017 &
0.021 \\
~se\_cl & 0.043 & 0.484 & 0.008 & 0.032 & 0.070 & 0.036 & 0.010 & 0.020
& 0.023 \\
Q75 & & & & & & & & & \\
~coeff & 0.031 & -1.258 & 0.033 & 0.153 & 0.104 & 0.616 & -0.036 & 0.008
& 0.006 \\
~se\_gls & 0.048 & 0.551 & 0.008 & 0.034 & 0.071 & 0.036 & 0.008 & 0.022
& 0.028 \\
~se\_r & 0.049 & 0.696 & 0.009 & 0.034 & 0.075 & 0.043 & 0.007 & 0.018 &
0.023 \\
~se\_cl & 0.039 & 0.919 & 0.012 & 0.041 & 0.079 & 0.055 & 0.010 & 0.022
& 0.020 \\
\end{longtable}

@@

Considering the estimated effects across quantiles, we observe few
differences in the reported GLS standard errors compared to the
analytical standard errors reported in MSS. Our clustered standard
errors, however, are closer to the bootstrap-based standard errors the
authors report.\footnote{The differences in the GLS standard errors may
  be due that in our derivation the influence function of the
  standardized \(\tau_{th}\) quantile (see \#eq-ifs) does not have the
  same leading term as the one reported in MSS (see Theorem 3, and the
  definition of \(W\)).}

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
  oneside]{article}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[lmargin=1.1in,rmargin=1.1in,tmargin=1in,bmargin=1.2in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

@@

% TODO: Add custom LaTeX header directives here
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{chicago}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments},
  pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
  pdfkeywords={Fixed effects, Linear heteroskedasticity, Location-scale
model, Quantile regression},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\definecolor{ahjcolor}{rgb}{0.0, 0.13, 0.82}
\PassOptionsToPackage{colorlinks=true, linkcolor=ahjcolor, urlcolor=ahjcolor, citecolor=ahjcolor}{hyperref}

% --- Packages ---
% Layout and spacing
\usepackage{setspace}
\usepackage{enumitem}

% Math and symbols
\usepackage{amsmath, amssymb, amsthm, amsbsy, amsfonts, mathrsfs, mathtools, bm, dsfont}

% Graphics and tables
\usepackage{graphicx, float, caption, subcaption}
\usepackage{longtable, array, multirow, booktabs, threeparttable}
\usepackage{lscape}

% Text formatting
\usepackage{color, xcolor, soul}
\usepackage{titlesec}

% Additional features
\usepackage{authblk} % Author and affiliation
\usepackage{appendix} % Appendix support

% Hyperlinks
\usepackage{hyperref}

% Math Operators
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\sign}{sign}
\DeclareMathOperator*{\tr}{Tr}
\DeclareMathOperator*{\p}{Pr}
\DeclareMathOperator*{\Var}{Var}
\DeclareMathOperator*{\rank}{rank}
\DeclareMathOperator*{\diag}{diag}

% Theorem Environments
\newtheorem{thm}{Theorem}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{ass}{Assumption}
\newtheorem{exm}{Example}

% Affiliation formatting
\renewcommand\Affilfont{\itshape\small}

% LaTeX tweaks
\setcounter{MaxMatrixCols}{10}
\makeatletter
\makeatother

% Page settings
\onehalfspacing
\setlength{\parskip}{0.5em}
\setlist{nolistsep}
% title

\title{\textbf{\Large Estimating Quantile Regressions with Multiple
Fixed Effects through Method of Moments}\thanks{The opinions expressed
in this paper are those of the authors and do not necessarily reflect
the views of the World Bank, its Board of Directors, or the countries it
represents.

The authors would like to thank Enrique Pinzon an Joao Santos-Silva for
their helpful comments and suggestions.}}

\author{
Fernando Rios-Avila
\thanks{
      Levy Economics Institute of Bard
College      \href{mailto:friosavi@levy.org}{Email: friosavi@levy.org}
  } \hspace{0.25 cm} 
Leonardo Siles
\thanks{
      Universidad Católica
Boliviana      \href{mailto:leonardo.siles@ucb.edu.bo}{Email: leonardo.siles@ucb.edu.bo}
  } \hspace{0.25 cm} 
Gustavo Canavire-Bacarreza
\thanks{
      The World
Bank      \href{mailto:gcanavire@worldbank.org}{Email: gcanavire@worldbank.org}
  }}

\begin{document}
\maketitle
\begin{abstract}

    This paper proposes a new method to estimate quantile regressions
with multiple fixed effects. The method, which expands on the strategy
proposed by \citet{mss2019}, allows for the inclusion of multiple fixed
effects and provides various alternatives for the estimation of standard
errors. We provide Monte Carlo simulations to show the finite sample
properties of the proposed method in the presence of two sets of fixed
effects. Finally, we apply the proposed method to estimate the
determinants of the surplus of government as a share of GDP, allowing
for both time and country fixed effects. \\ \\

    \noindent \textbf{Keywords:} Fixed effectsLinear
heteroskedasticityLocation-scale modelQuantile regression \\
    \noindent \textbf{JEL Codes:} C21C22C23

    \end{abstract}

    \newpage

@@

In principle, under the assumption that data-generating process behind
the data is based on a multiplicative heteroskedastic process that is
linear in parameters \citep[@he1997, @zhao2000, @cameron2005]{mss2019},
the effect of a variable \(X\) on the \(q_{th}\) quantile can be derived
as the combination of a location effect, and scale effect moderated by
the quantile of an underlying i.i.d. error. For statistical inference,
MSS derives the asymptotic distribution of the estimator, suggesting the
use of bootstrap standard errors, as well.

@@

\begin{table}[H]

@@

\section{Illustrative applications}\label{illustrative-applications}

\subsection{Determinants of government
surpluses}\label{determinants-of-government-surpluses}

@@

\begin{table}[h]

\caption{\label{tbl-tb1}Determinants of Government Surpluses: Individual
Fixed Effects}

    \centering
    \begin{tabular}{lccccccccc}
    \toprule
              & polityt &  lyp   & trade & p1564 &  p65   &  lspl  & oil-im & oil-ex &  ygap  \\
    \midrule
    \multicolumn{8}{l}{\textbf{Location}} \\
    \ \ \ coeff     &  0.116  & -0.715 & 0.030 & 0.121 & 0.028  & 0.691  & -0.047 & -0.006 & 0.010  \\
    \ \ \ se-gls   &  0.046  & 0.540  & 0.008 & 0.033 & 0.070  & 0.035  & 0.008  & 0.022  & 0.028  \\
    \ \ \ se-r     &  0.047  & 0.597  & 0.008 & 0.031 & 0.070  & 0.037  & 0.007  & 0.017  & 0.021  \\
    \ \ \ se-cl    &  0.046  & 0.465  & 0.007 & 0.032 & 0.071  & 0.035  & 0.010  & 0.020  & 0.023  \\
    \hline
    \multicolumn{8}{l}{\textbf{Scale}} \\
    \ \ \ coeff     & -0.097  & -0.616 & 0.003 & 0.036 & 0.087  & -0.085 & 0.013  & 0.016  & -0.004 \\
    \ \ \ se-gls   &  0.032  & 0.371  & 0.005 & 0.023 & 0.048  & 0.024  & 0.006  & 0.015  & 0.019  \\
    \ \ \ se-r     &  0.031  & 0.398  & 0.005 & 0.020 & 0.049  & 0.025  & 0.005  & 0.010  & 0.015  \\
    \ \ \ se-cl    &  0.048  & 0.800  & 0.008 & 0.031 & 0.067  & 0.029  & 0.004  & 0.010  & 0.012  \\
    \hline
    \multicolumn{8}{l}{\textbf{Q25}} \\
    \ \ \ coeff     &  0.191  & -0.239 & 0.028 & 0.093 & -0.039 & 0.756  & -0.057 & -0.018 & 0.013  \\
    \ \ \ se-gls   &  0.059  & 0.684  & 0.010 & 0.042 & 0.088  & 0.045  & 0.010  & 0.027  & 0.035  \\
    \ \ \ se-r     &  0.056  & 0.656  & 0.008 & 0.036 & 0.086  & 0.040  & 0.010  & 0.020  & 0.025  \\
    \ \ \ se-cl    &  0.073  & 0.687  & 0.006 & 0.041 & 0.098  & 0.023  & 0.010  & 0.021  & 0.029  \\
    \hline
    \multicolumn{8}{l}{\textbf{Q50}} \\
    \ \ \ coeff     &  0.108  & -0.765 & 0.030 & 0.124 & 0.035  & 0.684  & -0.046 & -0.005 & 0.009  \\
    \ \ \ se-gls   &  0.046  & 0.535  & 0.007 & 0.033 & 0.069  & 0.035  & 0.008  & 0.022  & 0.027  \\
    \ \ \ se-r     &  0.046  & 0.593  & 0.008 & 0.031 & 0.069  & 0.036  & 0.007  & 0.017  & 0.021  \\
    \ \ \ se-cl    &  0.043  & 0.484  & 0.008 & 0.032 & 0.070  & 0.036  & 0.010  & 0.020  & 0.023  \\
    \hline
    \multicolumn{8}{l}{\textbf{Q75}} \\
    \ \ \ coeff     &  0.031  & -1.258 & 0.033 & 0.153 & 0.104  & 0.616  & -0.036 & 0.008  & 0.006  \\
    \ \ \ se-gls   &  0.048  & 0.551  & 0.008 & 0.034 & 0.071  & 0.036  & 0.008  & 0.022  & 0.028  \\
    \ \ \ se-r     &  0.049  & 0.696  & 0.009 & 0.034 & 0.075  & 0.043  & 0.007  & 0.018  & 0.023  \\
    \ \ \ se-cl    &  0.039  & 0.919  & 0.012 & 0.041 & 0.079  & 0.055  & 0.010  & 0.022  & 0.020  \\
    \bottomrule
    \end{tabular}

@@

Considering the estimated effects across quantiles, we observe few
differences in the reported GLS standard errors compared to the
analytical standard errors reported in MSS. Our clustered standard
errors, however, are closer to the bootstrap-based standard errors the
authors report.\footnote{The differences in the GLS standard errors may
  be due that in our derivation the influence function of the
  standardized \(\tau_{th}\) quantile (see Equation~\ref{eq-ifs}) does
  not have the same leading term as the one reported in MSS (see Theorem
  3, and the definition of \(W\)).}

@@

\section{\texorpdfstring{Complementary analysis of
Section~\ref{sec-crime}}{Complementary analysis of Section~}}\label{sec-app-crime}

In this appendix, we present the quantile regressions of both (log)
per-capita household income and the (log) of labor income from main
occupation on the (log) of annual reported murders. While in the first
specification the coefficients of interest are not significant at
conventional levels because of clustered standard errors (see
Table~\ref{tbl-acrime1}), the same pattern of decreasing association
between murders and measurements of well-being as we move to the right
of the distribution is revealed using our proposed method.

However, in Table~\ref{tbl-acrime2} we get significant (at the 1\%
level) associations between reported murders and a slightly different
measurement of labor income that only takes into account the main
occupation of the individual. Compared to total labor income, the
coefficients displayed in Table~\ref{tbl-acrime2} are smaller in
magnitude: for the lowest decile of the distribution, we find a 1
percentage point difference in the coefficient of interest between the
two alternative specifications, where the largest effect corresponds to
total labor income. Nevertheless, and once again, the decreasing pattern
of reported murders across quantiles is documented for this
specification. What is even more interesting, compared to our
estimations in Table~\ref{tbl-ecuador}, is that crime is no longer
statistically meaningful from the median of the distribution onwards.

\begin{table}[H]

\caption{\label{tbl-acrime1}The Effect of Crime on Per Capita Household
Income: Canton and Time Fixed Effects}

    \centering
    \begin{tabular}{lccccc}
    \toprule
    VARIABLES & q10 & q25 & q50 & q75 & q90 \\ \hline
     &  &  &  &  &  \\
    lmurders & -0.026 & -0.022 & -0.019 & -0.015 & -0.012 \\
     & (0.019) & (0.015) & (0.012) & (0.009) & (0.008) \\
    age & 0.005*** & 0.005*** & 0.005*** & 0.006*** & 0.006*** \\
     & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) \\
    age$^2$ & 0.000 & 0.000 & 0.000** & 0.000** & 0.000** \\
     & (0.000) & (0.000) & (0.000) & (0.000) & (0.000) \\
    male & -0.014** & -0.010** & -0.006 & -0.003 & 0.000 \\
     & (0.006) & (0.005) & (0.004) & (0.004) & (0.004) \\
    informal & -0.428*** & -0.377*** & -0.326*** & -0.279*** & -0.237*** \\
     & (0.029) & (0.024) & (0.018) & (0.014) & (0.011) \\
    urban & 0.136*** & 0.128*** & 0.119*** & 0.112*** & 0.105*** \\
     & (0.033) & (0.030) & (0.028) & (0.026) & (0.025) \\
    Constant & 5.046*** & 5.377*** & 5.707*** & 6.014*** & 6.282*** \\
     & (0.079) & (0.068) & (0.061) & (0.058) & (0.059) \\
     &  &  &  &  &  \\ \hline
    Observations & 566,127 & 566,127 & 566,127 & 566,127 & 566,127 \\
    Canton FE & Yes & Yes & Yes & Yes & Yes \\
    Year FE & Yes & Yes & Yes & Yes & Yes \\ \hline
    \multicolumn{6}{c}{\footnotesize Clustered standard errors at Canton Level in parentheses} \\
    \multicolumn{6}{c}{\footnotesize *** p$<$0.01, ** p$<$0.05, * p$<$0.1} \\
    \multicolumn{6}{c}{\footnotesize Coefficients for marital status, education attainment and household size not shown.} \\
\end{tabular}

\begin{table}[H]

\caption{\label{tbl-acrime2}The Effect of Crime on Labor Income in Main
Occupation: Canton, Activity Sector and Time FE}

    \centering
    \begin{tabular}{lccccc}
    \toprule
    VARIABLES & q10 & q25 & q50 & q75 & q90 \\ \hline
     &  &  &  &  &  \\
    lmurders & -0.021*** & -0.014** & -0.007 & -0.002 & 0.004 \\
     & (0.008) & (0.006) & (0.005) & (0.006) & (0.007) \\
    age & 0.061*** & 0.053*** & 0.046*** & 0.040*** & 0.034*** \\
     & (0.003) & (0.002) & (0.002) & (0.001) & (0.001) \\
    age$^2$ & -0.001*** & -0.001*** & -0.000*** & -0.000*** & -0.000*** \\
     & (0.000) & (0.000) & (0.000) & (0.000) & (0.000) \\
    male & 0.158*** & 0.149*** & 0.141*** & 0.133*** & 0.126*** \\
     & (0.018) & (0.015) & (0.012) & (0.010) & (0.010) \\
    informal & -0.515*** & -0.460*** & -0.410*** & -0.363*** & -0.321*** \\
     & (0.018) & (0.015) & (0.013) & (0.012) & (0.012) \\
    urban & -0.091*** & -0.098*** & -0.105*** & -0.111*** & -0.116*** \\
     & (0.012) & (0.011) & (0.010) & (0.010) & (0.011) \\
    married & 0.099*** & 0.093*** & 0.087*** & 0.082*** & 0.077*** \\
     & (0.007) & (0.005) & (0.004) & (0.004) & (0.004) \\
    educ & 0.042*** & 0.046*** & 0.050*** & 0.053*** & 0.056*** \\
     & (0.001) & (0.002) & (0.003) & (0.004) & (0.005) \\
    tenure & 0.007*** & 0.006*** & 0.005*** & 0.005*** & 0.004*** \\
     & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) \\
    Constant & 3.882*** & 4.279*** & 4.649*** & 4.987*** & 5.294*** \\
     & (0.064) & (0.045) & (0.047) & (0.057) & (0.068) \\
     &  &  &  &  &  \\ \hline
    Observations & 249,993 & 249,993 & 249,993 & 249,993 & 249,993 \\
    Canton FE & Yes & Yes & Yes & Yes & Yes \\
    Activity Sector FE & Yes & Yes & Yes & Yes & Yes \\
    Year FE & Yes & Yes & Yes & Yes & Yes \\ \hline
    \multicolumn{6}{c}{ Clustered standard errors at Canton Level in parentheses} \\
    \multicolumn{6}{c}{ *** p$<$0.01, ** p$<$0.05, * p$<$0.1} \\
    \end{tabular}
